CRUSE to Safe Cycling in Ireland

### 2023-09-20 paper.qmd
Number sections

# Methods {#sec-methods}

@@

Methods were developed to overcome each of these, as outlined in the following subsections.

## Disaggregation of origin-destination data

@@

## Additional trip purposes

@@

## User interface

>>>>

# Methods and data {#sec-methods}

@@

Methods were developed to overcome each of these, as outlined in @sec-trip-purposes to @sec-ui.

## Disaggregation of origin-destination data {#sec-disaggregation}

A feature of active travel interventions is that they require dense networks of routes to be effective [TODO: cite parkin].
This means that high levels of geographic resolution are needed in the data used to estimate cycling potential.
However, datasets on travel patterns are often only available at the level of administrative zones.

@@

## Additional trip purposes {#sec-trip-purposes}

@@

## User interface {#sec-ui}
